A perfect storm and the natural endowments of trade-enabling infrastructure

### 2023-06-07 Slides/20min/20min.Rmd
Update slides
Fix STR table

.pull-right[
![STR_reg](Figures/STR_regressions.PNG)
*Larger on next page*
]

---
# The channel caused trade
![STR_reg](Figures/STR_regressions.PNG)

>>>>

.pull-right[
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/STR_regressions.png")
```
*Larger on next page*
]

---
# The channel caused trade
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/STR_regressions.png")
```
